Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-03 supp.rnw
Explain the supplementary partial residual plots in their captions.

	\caption{%
		Partial residual plots using the most parsimonious model.
	}
	\label{fig:partial-residual-best}
\end{figure}

@@

	\caption{%
		Partial residual plots using the model average model.
	}
	\label{fig:partial-residual-average}
\end{figure}

>>>>

	\caption{%
		Partial residual plots showing the effects of competition coefficients in the most parsimonious model.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
	}
	\label{fig:partial-residual-best}
\end{figure}

@@

	\caption{%
		Partial residual plots showing the effects of competition coefficients in model average model.
		Each plot shows the effect of the parameter $\alpha_{ij}$, where $i$ is the focal species for that row of plots, and $j$ is the competing species for that column of plots.
	}
	\label{fig:partial-residual-average}
\end{figure}
